Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-14 paper/ms.tex
Add more about what an action is

Since an azimuthal-dependent midplane is effectively a departure from a
perfectly axisymmetric potential, we In a slowly-evolving axisymmetric
potential, the actions of stars' orbits are conserved quantities
\citep{2008gady.book.....B,2014RvMP...86....1S}. In other words, if we could
measure the actions of a star in such a potential, we would measure the same
actions over the course of the orbit. The non-axisymmetries of a more
realistic potential induce time evolution in the {\em measured} actions ---
the true orbital invariants (if they exist) are invariant by definition.
Through simple tests, we will see that even in a truly axisymmetric potential,
if the wrong coordinate system is assumed then there will be additional time
evolution in the measured actions.

>>>>

Since an azimuthal-dependent midplane is effectively a departure from a
perfectly axisymmetric potential, we consider the effect that an erroneous
midplane has on the conservations of actions. The actions of an orbit are
typically computed in a cylindrical coordinate system as,
\beq\label{eq:actions}
J_i \equiv
\frac{1}{2\pi} \oint_{\text{orbit}}p_i\,\text{d}x_i\text{,}
\eeq
where $i=R,z,\phi$. Note that $J_{\phi} \equiv L_z$. In a slowly-evolving axisymmetric potential, the actions
of stars' orbits are conserved quantities
\citep{2008gady.book.....B,2014RvMP...86....1S}. The non-axisymmetries of a
more realistic potential induce time evolution in the {\em measured} actions
--- the true orbital invariants (if they exist) are invariant by definition.
Through simple tests, we will see that even in a truly axisymmetric potential,
if the wrong coordinate system is assumed then there will be additional time
evolution in the measured actions.
